---
title: "Making a shiny app"
author: "Alexander Wong"
date: "4/30/2020"
output: 
  rmarkdown::html_document:
    theme: darkly
runtime: shiny
---

# Shiny apps are a cool way to interact and visualize data
## They require no web development skills! Just R skillz!

Very useful tutorial on making Shiny web apps: <https://shiny.rstudio.com/tutorial/>

Check this link to put Shiny apps into Rmarkdown files to make beautiful interactive documents: <https://shiny.rstudio.com/articles/interactive-docs.html>

Writing Shiny apps in R markdown in a bit different than regular Shiny app writing (it's actually easier!). Be sure to put `runtime: shiny` in the YAML header.

You can also change the look of your document in the YAML header as well.

### It takes some time to learn the process but once you get the work flow it's that easy.

You can use the baseball data or your own data! Come up with a simple app to visualize or interact with your data!

```{r library and data}
library(shiny)
library(Lahman)
library(dplyr)
ModernTeams<- Lahman::Teams%>%
    filter(yearID>=1960)
```

```{r server.R, echo=FALSE}
titlePanel("Team Stats over the Years")
selectInput(inputId = "Type",
            label = "Statistic",
            choices = names(ModernTeams[,c(9,10,15:40)]))

selectInput(inputId = "team",
            label = "Team",
            choices = unique(ModernTeams$name))

        mainPanel(
           plotOutput("statPlot"),
           tags$a(href  = "http://www.seanlahman.com/baseball-archive/statistics/", "Data Source: Sean Lahman's Baseball Database")
        )
```

```{r index.html, echo=FALSE}
    SelectedTeams<- reactive({
        ModernTeams%>%
            filter(name == input$team)%>%
            select(yearID, input$Type)
    })

    output$statPlot <- renderPlot({
       plot(x=SelectedTeams()[[1]], y=SelectedTeams()[[2]], type = "l", xlab = "Season Year", ylab = input$Type)

    })
```